---
title: "October 7 Daily R"
author: "Ruth Holloway"
date: "10/7/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(MASS)
npk

#I got this code from the R documentation website and want to figure out what it does
options(contrasts = c("contr.sum", "contr.poly")) #setting a contrast is telling R what to do with categorical variables. contr.sum constrains variables so that they add up to zero. contr.poly is good for ordered variables. I wonder why we're using it here, because nitrogen, phosphorous, and potaassium aren't different orders of the same thing.
npk.aov <- aov(yield ~ block + N*P*K, npk) #this is an analysis of variance (ANOVA). the aov function fits a model (based on the contrasts we set?) 
npk.aov #this looks like it's estimating effects, which I didn't mean to do, but I'm already in this deep
summary(npk.aov) #I wonder why block is a good predictor of yield. isn't the idea generally to apply the same treatment to different blocks in order to compare treatment effects? or is block itself a treatment? 
coef(npk.aov) 
```

I went back and looked at the data and the blocks are not the same! I guess I didn't 
really understand all of the variables in this data when I started working with 
it. Basically, since differnt blocks apply four treatments with overlap between 
blocks, they're a good way to estimate the effects of the specific treatments. 
For instance, block three got treated with nitrogen whereas block four got treated 
with potassium. They both had one pea plant treated with all three elements, so 
we know that it isn't causing the variance. Thus, the difference must be because 
of the varying effects of nitrogen and potassium.