---
title: "September 22 Daily R"
author: "Ruth Holloway"
date: "9/22/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This is day 3 working with this data, and I really want to find a way to show
all of my relationships of interest on one chart. If my explanatory variables 
were continuous, this would be a lot easier! Yesterday, I did boxplots for each 
explanatory variable, but today I'm trying to combine them.

```{r}
#load data
library(readxl)
GSS <- read_excel("Data/GSS.xlsx")

#clean data
library(dplyr)
SocialSurvey<-subset(GSS, select=(3:5)) #remove ID and year
SocialSurvey$Income <- recode(SocialSurvey$Income, "Far below average" = 1, "Below average" = 2, "Average" = 3, "Above average" = 4, "Far above average" =5) #recode income variable
SocialSurvey$Income<-as.factor(SocialSurvey$Income) #turn income levels into factors

SocialSurvey
SocialSurvey$Prestige<-as.integer(SocialSurvey$Prestige) #convert type double to integer

#here's the relationships I'm looking at
lm(Prestige~Income, data=SocialSurvey)
lm(Prestige~Income+Children+Income*Children, data=SocialSurvey)

SocialSurvey$Child<-ifelse(SocialSurvey$Children>0,"Yes","No") #create binary variable for children
SS<-na.omit(SocialSurvey) #remove missing values
SS

#visualize data
library(ggplot2)
ggplot(SS, aes(x = Income, y = Prestige))+
  geom_bar(
    aes(fill = Prestige), stat = "identity", color = "white",
    position = position_dodge(0.9)
    )+
  facet_wrap(~Child)

```
So this is my first try showing two categories of data side by side, and I'm not 
displeased. It could be better. The prestige measure is a bit unclear, but basically 
the y axis is the "frequency" of certain job prestige levels. It's interesting 
because there's a negative relationship between the  number of children under 6 
and job prestige, but in this model, having any children under 6 seems to be 
related to higher levels of job prestige. If I had to guess, I'd say that it's 
job prestige that predicts having young children (feeling like one is able to 
support a family) and not the other way around.

#References
http://www.sthda.com/english/articles/32-r-graphics-essentials/129-visualizing-multivariate-categorical-data/


