---
title: "September 17 Daily R"
author: "Ruth Holloway"
date: "9/17/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(readxl)
USSR <- read_excel("Data/USSR - CPSU Politburo - 1922-1991.xlsx")
View(USSR)

#subset parts of data
USSRcleaned<-USSR[, c('ELITE_RETENURE','ELITE_EXITTYPE', 'ELITE_EXITFATE', 'ELITE_EXITLEADER', 'ELITE_OCCUPATION', 'ELITE_ETHNICITY')]
USSRcleaned<-na.omit(USSRcleaned)
USSRcleaned

lm(ELITE_RETENURE~ELITE_EXITFATE, data=USSRcleaned) #model indicates that exiled elites typically served less time than those who were executed, and that those who were not punished served the longest in office

#recode categorical variables for exit fate as factors
library(dplyr)
USSRcleaned$ELITE_EXITFATE <- recode(USSRcleaned$ELITE_EXITFATE, "No Punishment" = 0, "Exile" = 1, "Execution" = 2)

#visualize the exit fates of elites in the USSR
library(ggplot2)
ggplot(USSRcleaned, aes(x=ELITE_EXITFATE)) +
  geom_dotplot() #looks like the majority weren't punished, but that one was exiled and nine were executed

#examine under which leaders an outgoing elite was more likely to be executed
boxplot(ELITE_EXITFATE~ELITE_EXITLEADER, data=USSRcleaned) #one execution took place under Malenkov, but Stalin executed eight elites and exiled one

```

I'm finding that it's harder to interact meaningfully with categorical and factor 
data as opposed to numeric, at least in terms of how I've been taught in the past 
to think about and analyze data. Boxplots are kind of my go to when it comes to 
looking at ordinal variables, but I'm curious to find more ways that I can 
understand/analyze/visualize non-numeric observations.

# References
@data{DVN/QZ9BSA_2019,
author = {Matthews, Austin S.},
publisher = {Harvard Dataverse},
title = {{Authoritarian Ruling Elites Database (ARED)}},
UNF = {UNF:6:wCE6Fbq4fzjLGf3CGoYYXQ==},
year = {2019},
version = {V36},
doi = {10.7910/DVN/QZ9BSA},
url = {https://doi.org/10.7910/DVN/QZ9BSA}
}